Generalized Tractability

### 2023-04-21 GeneralizedTractability_230418.tex
Updates from Overleaf

Certain common notions of tractability are covered by the general situation described above.
\begin{equation*}
	\begin{array}{r@{\qquad}c@{\qquad}cc}
		& T(\varepsilon^{-1},d,\vp)
		& T(0,d,\vp)\\
		\toprule
		\text{strong polynomial algebraic  tractability} & \max(1,\varepsilon^{-p}) & 1\\
		\text{polynomial algebraic tractability} & \max(1,\varepsilon^{-p})d^{q} & d^{q}\\
		\text{strong polynomial exponential tractability} &  [\max(1,\log(1 + \varepsilon^{-1})]^p & 1\\
		\text{polynomial exponential tractability} &
		[\max(1,\log(1 + \varepsilon^{-1}))]^p  d^{q} & d^{q}
	\end{array}
\end{equation*}
Here above, $\vp = (p,q)$ in some cases. \peter{A general reference 
for results on algebraic tractability is \cite{NW08}, for exponential tractability we refer to \cite{HKW19} and \cite{KW19}.}

In the sections below we prove necessary and sufficient conditions on tractability as generally defined in \eqref{eq:tract_def} and \eqref{eq:strong_tract_def}.  These conditions involve the boundedness of sums defined in terms of $(T(\lambda_{i,d}^{-1},\cdot, \cdot))_{i=1}^\infty$.  In practice, it may be easier to verify whether or not these conditions hold than to verify \eqref{eq:tract_def and \eqref{eq:strong_tract_def}} directly.

>>>>

Certain common notions of tractability are covered by the general situation described above.
\begin{equation*}
	\begin{array}{r@{\qquad}c@{\qquad}cc}
		& T(\varepsilon^{-1},d,\vp)
		& T(0,d,\vp)\\
		\toprule
		\text{strong polynomial algebraic  tractability} & \max(1,\varepsilon^{-p}) & 1\\
		\text{polynomial algebraic tractability} & \max(1,\varepsilon^{-p})d^{q} & d^{q}\\
		\text{strong polynomial exponential tractability} &  [\max(1,\log(1 + \varepsilon^{-1})]^p & 1\\
		\text{polynomial exponential tractability} &
		[\max(1,\log(1 + \varepsilon^{-1}))]^p  d^{q} & d^{q}
	\end{array}
\end{equation*}
Here above, $\vp = (p,q)$ in some cases. A general reference 
for results on algebraic tractability is \cite{NW08}, for exponential tractability we refer to \cite{HKW19} and \cite{KW19}.

In the sections below we prove necessary and sufficient conditions on tractability as generally defined in \eqref{eq:tract_def} and \eqref{eq:strong_tract_def}.  These conditions involve the boundedness of sums defined in terms of $(T(\lambda_{i,d}^{-1},\cdot, \cdot))_{i=1}^\infty$.  In practice, it may be easier to verify whether or not these conditions hold than to verify \eqref{eq:tract_def} and \eqref{eq:strong_tract_def} directly.
